Continuous Generalization of Buildings \protect\\ by Growing and Merging

### 2017-08-11 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Springer/ContinuousGeneralisation_Paper_Springer.tex
removed some unused figures; added the description of Imai-Iri algorithm

\newcommand{\e}[1]{\times 10^{#1}}

@@

\title*{Continuous Generalization of Buildings}
\titlerunning{Continuous Generalization of Buildings}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Dongliang Peng and Guillaume Touya}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{
	Dongliang Peng 
	\at Chair of Computer Science I, University of W\"urzburg, 
	Germany \\
	\email{dongliang.peng@uni-wuerzburg.de}
	\and
	% 
	Guillaume Touya
	\at COGIT, IGN, France \\
	\email{guillaume.touya@ign.fr}
}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

@@

We tried simplifying using Douglas--Peucker algorithm \parencite{Douglas1973}, 
but we hoped to remove more points. We found that Imai--Iri 
algorithm \parencite{ImaiIri1988} fit our needs well.

Imai--Iri algorithm finds all the valid shortcuts, and then

>>>>

\newcommand{\e}[1]{\times 10^{#1}}
\newcommand{\fig}{Fig.~}
\newcommand{\eq}{Eq.~}

@@

\title*{Continuous Generalization of Buildings \protect\\ by Growing and 
Merging}
\titlerunning{Continuous Generalization of Buildings}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Dongliang Peng and Guillaume Touya}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{
	Dongliang Peng 
	\at Chair of Computer Science I, University of W\"urzburg, 
	Germany \\
	\email{dongliang.peng@uni-wuerzburg.de}
	\and
	% 
	Guillaume Touya
	\at COGIT, IGN, France \\
	\email{guillaume.touya@ign.fr}
}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

@@

We tried simplifying using Douglas--Peucker algorithm \parencite{Douglas1973}, 
but we hoped to remove more points. We found that the Imai--Iri 
algorithm \parencite{ImaiIri1988} fit our needs well. Although a version with a 
lower running time exists \parencite[see][]{Chan1992}, we implemented the basic 
version.

The Imai--Iri algorithm first finds all the valid shortcuts of a polyline.
For a sequence of points on a polyline, 
if their distances to their shortcut are 
at most specified value $\epsilon$, then the shortcut is valid (see 
\fig\ref{fig:ImaiIri_Shortcut}). 
Second, the algorithm finds a sequence of valid shortcuts, from the beginning 
of a polyline to the end, using breadth-first search.
The sequence of valid shortcuts is an approximation of the polyline, 
and has the least number of line segments.

\begin{figure}[tb]
	\centering
	\includegraphics{ImaiIri_Shortcut}
	\caption{Valid shortcut and invalid shortcut for Imai--Iri algorithm.}
	\label{fig:ImaiIri_Shortcut}
\end{figure}

We add three more constraints for a shortcut to be valid
when we use the Imai--Iri algorithm. 
That is, 
a shortcut is not allowed to intersect the boundary of the original building, 
is not allowed to intersect the boundary of the grown building, 
and must be inside the grown building.
For the first constraint, 
if a shortcut intersects the boundary of the original building, 
we will need to shrink the building, which we do not want.
For the second and the third constraints,
if a shortcut is outside the grown building,
we are not able to arrive at the shortcut by growing.
